Global patterns of forest autotrophic carbon fluxes

### 2020-01-20 manuscript/manuscript draft.Rmd
Table 2
#54

\newpage  
| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Gross Primary Production | NA | flux partitioning of eddy-covariance; $NPP$+$R_{auto}$ | 243 | 49 |
| $NPP$ | Net Primary Production | stem, foliage, coarse root, fine root, optionally others (e.g., branch, reproductive, understory) | $ANPP$ + $BNPP$ (majority); $GPP$-$R_{auto}$ | 92 | 42 |
| $ANPP$ | Aboveground Net Primary Production | stem, foliage, optionally others (e.g., branch, reproductive, understory) (**issues [52](https://github.com/forc-db/Global_Productivity/issues/52), [54](https://github.com/forc-db/Global_Productivity/issues/54)**) |$ANPP_{woody-stem}$ + $ANPP_{foliage}$ (+ others) | 256 | 80 |
| $ANPP_{woody-stem}$ | Net Primary Production of woody stems | woody stems down to DBH $\le$ 10cm (no branch turnover) | direct measurement of stem growth increment (**with recruitment?**) | 264 | 96 |
| $ANPP_{foliage}$ | Net Primary Production of foliage | foliage | direct measurement of litterfall | 98 | 49 |
| $BNPP_{root}$  | Belowground Net Primary Production | coarse and fine roots |  coarse roots estimated indirectly using allometries based on aboveground stem increment measures ; fine roots as below | 101 | 48 |
| $BNPP_{fine.root}$ | Net Primary Production of fine roots | fine roots | measurements combined one or more of the following: minirhizotrons, fine root turnover, soil cores, root ingrowth cores | 88 | 41 |
| $R_{root}$ | Root Respiration | **coarse** and fine roots | *measurement of root gas exchange, root exclusion from soil respiration chambers* | 64 | 26 |
| $R_{auto}$ | Autotrophic Respiration | foliage, stem, and root | chamber measurements of component gas exchange | 22 | 13 |

@@

*Methodological consistency.* The data in ForC is derived from a range of studies, often employing different methods. For this reason, criteria were introduced to standardise for differences in methodology. Where data was based on forest plot census measurements, studies which used a minimum diameter at breast height (DBH) measure of >10cm were excluded from analysis.  It would be preferable to standardise by minimum area sampled; however x% of plots in the database are 1 ha or under in size; excluding these plots would place significant constraints on sample size. (**really, we didn't exclude any studies based on methodology (all studies measured min DBH 10 or less... ) so this paragraph needs revision. Also, address whether we standardize for inclusion/ exclusion of recruitment, and address branchfall.**)

>>>>

\newpage  
| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Gross Primary Production | NA | flux partitioning of eddy-covariance; $NPP$+$R_{auto}$ | 243 | 49 |
| $NPP$ | Net Primary Production | stem, foliage, coarse root, fine root, optionally others (e.g., branch, reproductive, understory) | $ANPP$ + $BNPP$ (majority); $GPP$-$R_{auto}$ | 92 | 42 |
| $ANPP$ | Aboveground Net Primary Production | stem, foliage, optionally others (e.g., branch, reproductive, understory) |$ANPP_{woody-stem}$ + $ANPP_{foliage}$ (+ others) | 256 | 80 |
| $ANPP_{woody-stem}$ | Woody stem growth component of $ANPP$ | woody stems down to DBH $\le$ 10cm (no branch turnover) | stem growth measurements scaled to biomass using allometries | 264 | 96 |
| $ANPP_{foliage}$ | Foliage component of $ANPP$ | foliage | litterfall collection (separated into components) | 98 | 49 |
| $BNPP$  | Belowground Net Primary Production | coarse and fine roots |  coarse roots estimated indirectly using allometries based on aboveground stem increment measures ; fine roots as below | 101 | 48 |
| $BNPP_{fine.root}$ | Fine root component of $BNPP$ | fine roots | measurements combined one or more of the following: minirhizotrons, fine root turnover, soil cores, root ingrowth cores | 88 | 41 |
| $R_{root}$ | Root Respiration | coarse and fine roots | partitioning of total soil respiration (e.g., through root exclusion), scaling of root gas exchange | 64 | 26 |
| $R_{auto}$ | Autotrophic Respiration | foliage, stem, and root | chamber measurements of component gas exchange | 22 | 13 |

@@

*Methodological consistency.* The data in ForC is derived from a range of studies, often employing different methods. For this reason, criteria were introduced to standardise for differences in methodology. Where data was based on forest plot census measurements, studies which used a minimum diameter at breast height (DBH) measure of >10cm were excluded from analysis.  It would be preferable to standardise by minimum area sampled; however x% of plots in the database are 1 ha or under in size; excluding these plots would place significant constraints on sample size. (**really, we didn't exclude any studies based on methodology (except soil respiration. all studies measured min DBH 10 or less... ), so this paragraph needs revision. Also, address whether we standardize for inclusion/ exclusion of recruitment.**)
- recruitment preferred when an option, did not review whether all included recruitment
- excluded alkali absoption and soda lime methods for estimating soil / root respiration
